Playfair and the \"Flatten the Curve\" Graphic

### 2022-02-19 _posts/2022-02-19-playfair-and-the-flatten-the-curve-graphic/playfair-and-the-flatten-the-curve-graphic.Rmd
build

One of the early tidbits from [Edward Tufte](https://www.edwardtufte.com)'s "[The Visual Display of Quantitative Information](https://www.edwardtufte.com/tufte/books_vdqi)" is this quote from Scottish political economist William Playfair's 1786 book "The Commercial and Political Atlas":

>>>>

One of the good early tidbits from [Edward Tufte](https://www.edwardtufte.com)'s "[The Visual Display of Quantitative Information](https://www.edwardtufte.com/tufte/books_vdqi)" is this quote from Scottish political economist William Playfair's 1786 book "The Commercial and Political Atlas":
